My title

### 2024-03-12 paper/paper.qmd
Update paper.qmd

```{r}
#| echo: false
#| message: false
#| warning: false
#run the regression model using glm.
# gender, age_groups, race, stateicp, education_level and hispanic are used to 
# predit whether a person will vote biden or not

model <- survey_model

>>>>

```{r}
#| echo: false
#| message: false
#| warning: false
model <- survey_model
